Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models

### 2020-10-14 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, add one more figure.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|r|}
\hline
Language Model 	& Dataset & Accuracy \\
\hline\hline
RoBERTa-wwm-ext-large & Case-2	&	99.8\% \\
RoBERTa-wwm-ext-large & Case-4	&	99.76\% \\
RBTL3  & Case-4	&	96.35\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on different dataset in the document classification task.}
\end{table}
%-------------------------------------------------------------------------

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 6	&	99.74\% \\
RBTL3  & CIFAR-10 & 6	&	99.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
\hline
RBT3   & CIFAR-100 & 6	&	99.74\% \\
RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large.}
\end{table}

@@

TThis paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{|l|c|r|}
\hline
Language Model 	& Dataset & Accuracy \\
\hline\hline
RoBERTa-wwm-ext-large & Case-2	&	99.80\% \\
RoBERTa-wwm-ext-large & Case-4	&	99.76\% \\
RBTL3  & Case-4	&	96.35\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on different dataset in the document classification task.}
\end{table}
%-------------------------------------------------------------------------

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 6	&	99.74\% \\
RBTL3  & CIFAR-10 & 6	&	99.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
\hline
RBT3   & CIFAR-100 & 6	&	93.71\% \\
RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large.}
\end{table}

@@

 This paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
